A Component-Based Sensor Network for \\ Environmental Monitoring

### 2009-03-12 docs/icccn2009/paper.tex
Updated the YSI Sonde Component subsection.
git-svn-id: svn://localhost/netbeams/trunk@364 559edde2-a4d4-44e0-96fc-4035e40d7396

Our implementation of the DSP is based on the Open Source
implementation of OSGi called Knopflerfish \cite{knopflerfish01}. Since Sun
Microsystems does not support its JDK for the Gumstix, we use JamVM
\cite{jamvm01} as the Java virtual machine implementation and GNU Classpath
\cite{classpath01} for the runtime libraries. We have implemented various DSP
Components that implement the functionality needed for NetBEAMS. On
the far left of Figure \ref{FIG_NETBEAMS} is the actual sensor; in our
case the aforementioned YSI Sonde. A YSI Sonde data producer (1) is a DSP
component that uses the RS232 standard to read the physical measurements from
the device over a serial port. This component converts the physical measurements 
into a DSP-specific message. The following XML Schema defines the YSI Sonde
specific message that captures all measurement points mentioned in
Table \ref{TAB_SONDE_MEASUREMENTS}:

\begin{code}
<xs:schema ...>
<xs:import schemaLocation="dsp-message.xsd"/>

<xs:element name="SondeDataMessage">
  <xs:complexType>
    <xs:complexContent>
      <xs:extension base="DSPMessage">
        <xs:sequence maxOccurs="unbounded"
                     minOccurs="1">
          <xs:element name="sondeData"
                      type="sondeDataType"/>
        </xs:sequence>
      </xs:extension>
    </xs:complexContent>
  </xs:complexType>
</xs:element>

<xs:complexType name="sondeDataType">
  <xs:sequence>
    <xs:element name="Date" type="xs:date"/>
    <xs:element name="Time" type="xs:time"/>
    <xs:element name="Temp" type="xs:float"/>
    <xs:element name="SpCond" type="xs:float"/>
    <!-- ... -->
  </xs:sequence>
</xs:complexType>
</xs:schema>
\end{code}

The schema is derived from DSPMessage. As a payload it adds an
unbounded sequence of sondeDataType. Each instance of this type
captures one timestamped measure point.

The YSI Sonde component can be
configured via special DSP messages that define properties such as the
sampling frequency. These property messages originate from the web
frontend that we will explain in a subsequent section.

>>>>

Our implementation of the DSP is based on the Open Source
implementation of OSGi called Knopflerfish \cite{knopflerfish01}. Since Sun
Microsystems does not support its JDK for the Gumstix, we use JamVM
\cite{jamvm01} as the Java virtual machine implementation and GNU Classpath
\cite{classpath01} for the runtime libraries. We have implemented various DSP
Components that implement the functionality needed for NetBEAMS. On
the far left of Figure \ref{FIG_NETBEAMS} is the actual sensor; in our
case the aforementioned YSI Sonde. A YSI Sonde data producer (1) is a DSP
component that uses the RS232 standard to read the physical measurements from
the device over a serial port. This component converts the physical measurements 
into a DSP-specific message. The following XML Schema defines the YSI Sonde's
specific message format which includes each measurement data point, described in
Table \ref{TAB_SONDE_MEASUREMENTS}, and its type:

\begin{code}
<?xml version="1.0" encoding="UTF-8"?>
<xs:schema targetNamespace="http://www.netbeams.dsp.org/sondedata.xsd" xmlns:jaxb="http://java.sun.com/xml/ns/jaxb" jaxb:version="2.0" xmlns:mc="http://www.netbeams.dsp.org/message.xsd" xmlns:sndata="http://www.netbeams.dsp.org/sondedata.xsd" xmlns:xs="http://www.w3.org/2001/XMLSchema">

    <xs:import namespace="http://www.netbeams.dsp.org/message.xsd" schemaLocation="message-content.xsd"/>

    <xs:annotation><xs:appinfo>
    <jaxb:globalBindings>
      <jaxb:javaType name="java.util.Calendar" xmlType="xs:date"
        parseMethod="javax.xml.bind.DatatypeConverter.parseDate"
        printMethod="javax.xml.bind.DatatypeConverter.printDate"
        />
      <jaxb:javaType name="java.util.Calendar" xmlType="xs:time"
        parseMethod="javax.xml.bind.DatatypeConverter.parseDate"
        printMethod="javax.xml.bind.DatatypeConverter.printDate"
        />
    </jaxb:globalBindings>
    </xs:appinfo></xs:annotation>

    <xs:element name="SondeDataMessage">
    <xs:complexType>
        <xs:complexContent>
            <xs:extension base="mc:AbstractMessageContent">
                <xs:sequence maxOccurs="unbounded" minOccurs="1">
                    <xs:element name="sondeData"
                        type="sndata:sondeDataType" />
                </xs:sequence>
                <xs:attribute name="date" type="xs:date"></xs:attribute>
                <xs:attribute name="time" type="xs:time"></xs:attribute>
            </xs:extension>
        </xs:complexContent>
    </xs:complexType>
    </xs:element>

    <xs:complexType name="sondeDataType">
        <xs:sequence>
                <xs:element name="Temp" type="xs:float"/>
                <xs:element name="SpCond" type="xs:float"/>
                <xs:element name="Cond" type="xs:float"/>
                <xs:element name="Resist" type="xs:float"/>
                <xs:element name="Sal" type="xs:float"/>
                <xs:element name="Press" type="xs:float"/>
                <xs:element name="Depth" type="xs:float"/>
                <xs:element name="pH" type="xs:float"/>
                <xs:element name="phmV" type="xs:float"/>
                <xs:element name="ODOSat" type="xs:float"/>
                <xs:element name="ODOConc" type="xs:float"/>
                <xs:element name="Turbid" type="xs:float"/>
                <xs:element name="Battery" type="xs:float"/>
        </xs:sequence>
  </xs:complexType>
</xs:schema>
\end{code}

The schema describes two Java classes, sondeDataType and SondeDataMessage, 
which are used to package the Sonde's incoming data into a DSP message for delivery 
to a remote consumer.  The SondeDataMessage class extends the AbstractMessageContent 
class by adding a new type to the message payload, SondeDataType.  Each time the Sonde
transmits its payload of measurement data during a sampling interval, the data is converted 
into a SondeDataType which is then encapsulated within SondeDataMessage and then sent 
to a remote consumer.

The YSI Sonde component can also be configured via special DSP messages, to direct the 
Sonde to change its sampling frequency.  These property messages originate from the web 
frontend that we will explained in a subsequent section.
